BHPWAVE: An adiabatic gravitational waveform model for compact objects undergoing quasi-circular inspirals into rotating massive black holes

### 2023-08-21 ms.tex

We can understand the relative impact of these self-forces on EMRI gravitational waveforms by expanding the phasing of the EMRI gravitational waveform $\Phi_\mathrm{GW}$ in powers of $\epsilon$ via a two-timescale analysis \cite{HindFlan08},
\begin{align}
\Phi_\mathrm{GW} = \frac{1}{\epsilon} \left[ \Phi_\mathrm{0PA} + \epsilon^{1/2} \Phi_\mathrm{res} + \epsilon \Phi_\mathrm{1PA} + O(\epsilon^2)\right].
\end{align}
The leading-order \emph{adiabatic} term\footnote{This term is also referred to as the post-0 adiabatic or 0PA term to remain consistent with the naming conventions of the sub-leading terms (e.g., $\Phi_\mathrm{1PA}$).} $\Phi_\mathrm{0PA}$ only depends on the time-averaged \emph{dissipative} first-order GSF, which drives the dissipation of energy and angular momentum from the system. The sub-leading post-1 adiabatic (1PA) piece $\Phi_\mathrm{1PA}$ depends on the remaining contributions from the first-order GSF and the time-averaged components of the second-order GSF. The half-order correction $\Phi_\mathrm{res}$ arises due to the presence of self-forced $r\theta$-resonances experienced by EMRIs undergoing eccentric and inclined inspirals \cite{FlanHind12}. EMRI gravitational models must, therefore, include the $\Phi_\mathrm{0PA}$, $\Phi_\mathrm{res}$, and $\Phi_\mathrm{1PA}$ effects in order to maintain sub-radian phase accuracy and enable the full scientific potential of future mHz gravitational wave observatories.

Nonetheless purely adiabatic models---which only include $\Phi_\mathrm{0PA}$ in the gravitational wave phasing---may be suitable for detecting (but not characterizing) EMRI signals and are invaluable tools for developing data analysis pipelines for EMRI search and parametrization. They capture almost all of the phasing information and relativistic behavior of EMRI signals, making them powerful probes of astrophysical parameter space. The theoretical foundation and numerical calculation of adiabatic waveforms is also well understood, and has been performed for the most generic, eccentric, precessing EMRIs \cite{HughETC21}.

@@

Therefore we introduce \texttt{bhpwave} [RTD link?] an open-source Python-based waveform generator that models the adiabatic dynamics and gravitational wave signals produced by a small body undergoing a quasi-circular\footnote{Quasi-circular refers to the fact that the particle is inspiraling so its motion is not circular, but at any moment of time its motion is tangent to a circular geodesic as described in Sec.~\ref{sec:adiabatic}. This is a consequence of the fact that in the adiabatic limit, circular orbits remain circular \cite{KennOri96, Kenn98}.} (non-eccentric) inspiral into a \emph{rotating} massive black hole. This code can model any binary with an initial orbital separation of $r_0 \leq 50 M$ and a massive black hole spin in the range $|a| \leq 0.995 M$. (See Sec.~\ref{sec:adiabatic} for exact definitions of $a$ and $r_0$.) Furthermore, the model supports any mass-ratio, though adiabatic waveform models are most relevant for $\epsilon \lesssim 10^{-4}$. By leveraging parallel computations across CPUs, \texttt{bhpwave} can evaluate years-long waveforms in milliseconds. Even on a standard laptop, waveform evaluations still complete within a few hundred milliseconds to a couple seconds.

@@

Additionally, \texttt{bhpwave} does not provide the first adiabatic calculation of quasi-circular inspirals. These systems have long been studied in the literature \cite{Detw78, KennOri96, FinnThor00, Hugh00b, GralHughWarb16}. However, as aforementioned, it is challenging to implement an adiabatic model that is efficient, reliable, and accessible. Even when neglecting eccentricity, the inclusion of massive black hole spin presents a number of challenges that are less pronounced for binaries with non-spinning bodies, such as the larger range of radial separations accessible to spinning systems, the faster frequency evolution for more deeply bound orbits, and the higher mode content needed for modeling rapidly-rotating systems. By building upon the theoretical foundations described in the literature, our aim for \texttt{bhpwave} is to provide an efficient and accessible model that fills in this area of parameter space and provides an important stepping stone for developing more advanced models that incorporate all possible orbital effects.

@@

The mass $\mu$ follows a geodesic $z_p^\mu \doteq (t_p, r_p, \theta_p, \phi_p)$ that maintains a constant Boyer-Lindquist radius $r_p = r_0$ and is restricted to the equatorial plane $\theta_p = \pi/2$ (with respect to the angular momentum of the Kerr black hole). Due to the Killing symmetries of Kerr spacetime, this motion possesses three constants of motion: the orbital energy $u_t = - \mathcal{E}$, the $z$-component of the orbital angular momentum $u_\phi = \mathcal{L}_z$, and the Carter constant $\mathcal{Q} = Q_{\mu\nu} u^\mu u^\nu$, which are related to $a$ and $r_0$ by
\begin{subequations} \label{eqn:En}
\begin{align}
    \mathcal{E} &= \frac{1 - 2 v^2 \pm \hat{a} v^3}{\sqrt{1-3v^2\pm 2\hat{a}v^3}},
    \\
    \mathcal{L}_z &= \pm M  \frac{1 \mp 2 \hat{a} v^3 + \hat{a}^2 v^4}{v\sqrt{1-3v^2\pm 2\hat{a}v^3}},
    \\
    \mathcal{Q} &= 0,
\end{align}
\end{subequations}
where $\hat{a} \equiv a/M$, $v^2 = M/r_0$, and $+$ ($-$) refers to prograde (retrograde) orbits.

@@

The spin-weighted spheroidal harmonics can be conveniently represented as a rapidly-converging series of spin-weighted spherical harmonics $Y_{s\ell m}$ \cite{Hugh00b},
\begin{align}
    S_{sjm}(\theta, \gamma)e^{im\phi} = \sum_{\ell=\ell_\mathrm{min}}^\infty b_{sjm}^\ell(\gamma) Y_{s\ell m}(\theta,\phi),
\end{align}
where $\ell_\mathrm{min}=\mathrm{max}[|m|,|s|]$. This decomposition is particularly useful because it allows us to reproject $\psi_4$ onto an angular basis that is independent of frequency,
\begin{align} \label{eqn:psi4LModes}
    \psi_4 = \rho^{4} \sum_{\ell=2}^\infty \sum_{m=-\ell}^\ell X_{-2\ell m}(r) e^{-im\Omega_pt} Y_{-2\ell m}(\theta, \phi),
\end{align}
where
\begin{align} \label{eqn:XfromR}
    X_{-2\ell m}(r) \sum_{j=\ell_\mathrm{min}}^\infty b_{-2jm}^\ell(\gamma)R_{-2jm}(r).
\end{align}
Furthermore, the spin-weighted spherical harmonics form a complete and orthonormal set of basis functions of the unit sphere (for the same value of spin-weight),
\begin{align}
    \int Y_{s\ell m} \bar{Y}_{s\ell'm'} d\Omega = \delta_{l l'} \delta_{m m'}.
\end{align}

@@

For our point-particle source on a circular geodesic, the radial mode function $R_{-2jm}(r)$ have the asymptotic forms
\begin{subequations} \label{eqn:asympR}
\begin{align}
    R_{-2jm}(r\rightarrow r_+) &\simeq Z^\mathcal{H}_{-2jm} \Delta^{2} e^{-im k_p r_*},
    \\ 
    R_{-2jm}(r\rightarrow \infty) &\simeq Z^\mathcal{I}_{-2jm} r^{3} e^{+im\Omega_p r_*},
\end{align}
\end{subequations}
where $k_p = \Omega_p - \Omega_+$, $\Omega_+ = a/(2Mr_+)$, and the tortoise coordinate $r_*$ is given by the differential relation $dr_*/dr = (r^2+a^2)/\Delta$.
The amplitudes $Z^\mathcal{H/I}_{-2jm}$ are often referred to as \emph{Teukolsky amplitudes} and are constructed via the standard Green's function method, also known as the method of variation of parameters (see Sec.~III\,A in \cite{HughETC21} or \cite{DrasHugh06} for further details). From \eqref{eqn:XfromR}, we see that $X_{-2\ell m}$ then possesses the same asymptotic behavior as $R_{-2\ell m}$ in \eqref{eqn:asympR} but with modified amplitudes
\begin{align}
    Z^\mathrm{H/I}_{-2jm} \rightarrow X^\mathrm{H/I}_{-2\ell m} = \sum_{j=\ell_\mathrm{min}}^\infty b^\ell_{-2jm}(\gamma) Z^\mathrm{H/I}_{-2jm}.
\end{align}
As a final note, because $Z^\mathrm{H/I}_{-2jm}$ and  $X^\mathrm{H/I}_{-2\ell m}$ depend on the source motion, we can parametrize both amplitudes in terms of the orbital constants, e.g., $X^\mathcal{H/I}_{-2\ell m}= {X}^\mathcal{H/I}_{-2ell m}(\Omega_p; a)$.

Upon obtaining $\psi_4$, we can then calculate the flux of energy that this radiative field carries away to infinity $\dot{E}^\mathcal{I}$ and the flux radiated down the black hole horizon $\dot{E}^\mathcal{H}$ \cite{TeukPres74}, 
\begin{subequations} \label{eqn:fluxes}
\begin{align}
    \dot{E}^\mathcal{I} &= \frac{1}{4\pi} \sum_{jm} \alpha_{jm}^\infty {|Z^\mathcal{I}_{-2jm}|^2},
    \\
    \dot{E}^\mathcal{H} &= \frac{1}{4\pi} \sum_{jm} \alpha_{jm}^\mathcal{H} {|Z^\mathcal{H}_{-2jm}|^2},
\end{align}
\end{subequations}
where 
\begin{align*}
    \alpha_{jm}^\mathcal{I} &= \frac{1}{m^2\Omega_p^2},
    \\
    \alpha_{jm}^\mathcal{H} &= \frac{256m^2 k_p\Omega_p(2Mr_+)^5(m^2k_p^2+4\epsilon^2)(m^2k_p^2+16\epsilon^2)}{|C_{2jm}|^2},
\end{align*}
$\epsilon = (r_+ - M)/(2Mr_+)$, and the Teukolsky-Starobinsky constant is given by
\begin{align} 
    |C_{2jm}|^2 &=\Lambda_{2j m }^2(\Lambda_{2j m }-2)^2
    \\ \notag
    & \quad + 8 a m^2 \Omega_p(1 - a \Omega_p)(\Lambda_{2j m }-2)(5\Lambda_{2j m }-4)
    \\ \notag
    & \quad \quad
    +48 (a m \Omega_p)^2[4(\Lambda_{2j m }-1)+3m(1- a \Omega_p)].
\end{align}
Note that the Chandrasekhar eigenvalue $\Lambda_{sjm} = \lambda_{sjm} + s(s+1)$ is invariant under the interchange $s\rightarrow -s$ \cite{Chan83}.
The angular momentum fluxes are then related to the energy fluxes by $\dot{L}_z^{\mathcal{I}/\mathcal{H}} = \Omega^{-1} \dot{E}^{\mathcal{I}/\mathcal{H}}$, leading to the total gravitational wave fluxes
\begin{align}
    \dot{E}^\mathrm{GW} &= \dot{E}^\mathcal{I} + \dot{E}^\mathcal{H},
    &
    \dot{L}_z^\mathrm{GW} &= \dot{L}_z^\mathcal{I} + \dot{L}_z^\mathcal{H}.
\end{align}

@@

Due to gravitational {radiation-reaction}, the small body does not remain on a circular geodesic. The binary \emph{radiates} gravitational waves and the small body \emph{reacts} to the radiative losses of energy and angular momentum by undergoing a quasi-circular inspiral into the rotating massive black hole. We can parametrize this motion in terms of the time-evolving orbital energy ${E}(t)$ and orbital phase $\Phi(t)$ of the inspiraling body, which at leading order is given by the equations of motion \cite{PounWard20,HughETC21},
\begin{align} \label{eqn:eom}
    \frac{d {E}}{dt} &= \epsilon \mathcal{F}_t + O(\epsilon^2),
    &
    \frac{d\Phi}{dt} &= \Omega + O(\epsilon).
\end{align}
Because $\dot{E} \sim \epsilon$, the orbital energy evolves gradually and the evolution can be understood in terms of the \emph{osculating geodesics} method \cite{GairETC11}. At any time $t_0$, the motion is approximately tangent to a geodesic with energy $E(t_0) \approx \mathcal{E}$ and frequency $\Omega(t_0) \approx \Omega_p$. The small body then evolves from geodesic to geodesic based on its gravitational wave emission until the body approaches the ISCO, at which point the approximation breaks down and we end the evolution.

In effect, at leading order we can express the orbital frequency $\Omega$ in terms of the orbital energy ${E}$ using Eqs.~\eqref{eqn:En} and \eqref{eqn:OmegaOfR}, but with $\mathcal{E}$ and $\Omega_p$ replaced by $E$ and $\Omega$, respectively. Furthermore, the forcing term $\mathcal{F}_t$ is constructed using flux-balance arguments \cite{Mino03, Galt82, QuinWald99}: the loss of orbital energy is balanced by the energy flux due to gravitational wave radiation produced by a point-particle on a circular geodesic $\dot{E}^\mathrm{GW}$, leading to the relation $\epsilon \mathcal{F}_t = - \dot{E}^\mathrm{GW}$.

As seen from Eq.~\eqref{eqn:eom}, the time it takes the system to undergo this inspiral scales with the radiation reaction timescale $T_\mathrm{insp} \sim T_\mathrm{rr} = M \epsilon^{-1}$. Similarly, the total accumulated phase scales like $\Delta\Phi_\mathrm{insp} \sim \epsilon^{-1}$.

@@

After determining the adiabatic inspiral of the smaller body, we generalize \eqref{eqn:psi4LModes}---our geodesic expression for $\psi_4$---by once again leveraging the fact that at any moment of time the motion is approximately tangent to a geodesic. Consequently, the field amplitudes slowly evolve with frequency and time $X^\mathcal{H/I}_{-2\ell m}(\Omega_p; a) \rightarrow X^\mathcal{H/I}_{-2\ell m}(\Omega(t); a)$, while the field's phase rapidly accumulates in proportion to the orbital phase $\Omega_p t \rightarrow \Phi(t)$. As a result, the adiabatic waveform $h = h_+ - i h_\times$ takes the form
\begin{align} \label{eqn:adiabaticWaveform}
    h(u,r,\theta,\phi) = \frac{\mu}{r}\sum_{\ell m} B_{\ell m}(u) Y_{-2\ell m}(\theta, \phi) e^{-im\Phi(u)},
\end{align}
where, assuming $r \gg M$, the waveform amplitudes are given by
\begin{align} \label{eqn:amplitude}
    B_{\ell m}(u) = -2\frac{X_{-2\ell m}^\mathcal{I}( \Omega(u);a)}{m^2\Omega^2(u)} = A_{\ell m} e^{i \psi_{\ell m}}.
\end{align}
For later convenience we introduce $A_{\ell m} = |B_{\ell m}|$, the magnitude of the waveform amplitudes, and $\psi_{\ell m}$, the phase of the complex amplitudes, both of which depend on $\Omega(u)$ and $a$. Furthermore, rather than using the conventions of \cite{KatzETC21,HughETC21}, we follow \cite{PounWard20} and parametrize the adiabatic waveform in terms of the outgoing time-coordinate $u=t-r_*$. As a result, if we hold the orbital constants and frequencies fixed, \eqref{eqn:adiabaticWaveform} reduces to a geodesic ``snapshot'' waveform obtained via \eqref{eqn:psi4ToH} and \eqref{eqn:psi4LModes}. In practice, when implementing \eqref{eqn:adiabaticWaveform} in \texttt{bhpwave}, we replace $u$ with Boyer-Lindquist time $t$ to match the FEW model (which is described by (10) in \cite{KatzETC21}). This is equivalent to parametrizing all of our waveforms with an initial time $t_0 = r_*$.

@@

The amplitude and phase decomposition of \eqref{eqn:adiabaticWaveform} makes it particularly straightforward to represent our waveforms in the frequency domain via the stationary phase approximation \cite{HughETC21},
\begin{align}
    \tilde{h}(f) &= \int_{-\infty}^\infty h(t) e^{2\pi i f t} dt,
    \\ \notag
    & \approx \frac{\mu}{r}\sum_{\ell m} \tilde{B}_{\ell m}(f) Y_{-2\ell m}(\theta, \phi) e^{i[2\pi f t_p(f)- m\Phi(t_p(f))]},
\end{align}
where
\begin{align} \label{eqn:fourierAmplitude}
    \tilde{B}_{\ell m}(f) \approx \sqrt{\frac{2\pi}{i m \dot{\Omega}[t_p(f)]}} {B}_{\ell m}(t_p(f)),
\end{align}
and $t_p(f)$ refers to the times at which the binary emits gravitational waves with frequency $f$. For each $(\ell, m)$-mode, time and frequency are approximately related by
\begin{align} \label{eqn:fourierPhase}
    2\pi f \approx m \dot{\Phi}(t) = m \Omega(t),
\end{align}
which we can invert to approximate $t_p(f)$ for individual harmonics. As explained in Appendix \ref{app:fourierPhase}, both \eqref{eqn:fourierAmplitude} and \eqref{eqn:fourierPhase} neglect terms related to $\dot{\psi}_{\ell m}$ and $\ddot{\psi}_{\ell m}$, which introduces an $O(\epsilon)$ error to the phase and an $O(\epsilon^{1/2})$ error to the amplitude. Since the amplitudes scale as $\tilde{B}_{\ell m}(f) \sim 1/\sqrt{\epsilon}$, it is safe to neglect these terms for small mass-ratios.

@@

\subsection{Fluxes and inspiral}

>>>>

We can understand the relative impact of these self-forces on EMRI gravitational waveforms by expanding the phasing of the EMRI gravitational waveform $\Phi_\mathrm{GW}$ in powers of $\epsilon$ via a two-timescale analysis \cite{HindFlan08},
\begin{align} \label{eqn:twotimescale}
\Phi_\mathrm{GW} = \frac{1}{\epsilon} \left[ \Phi_\mathrm{0PA} + \epsilon^{1/2} \Phi_\mathrm{res} + \epsilon \Phi_\mathrm{1PA} + O(\epsilon^2)\right].
\end{align}
The leading-order \emph{adiabatic} term\footnote{This term is also referred to as the post-0 adiabatic or 0PA term to remain consistent with the naming conventions of the sub-leading terms (e.g., $\Phi_\mathrm{1PA}$).} $\Phi_\mathrm{0PA}$ only depends on the time-averaged \emph{dissipative} first-order GSF, which drives the dissipation of energy and angular momentum from the system. The sub-leading post-1 adiabatic (1PA) piece $\Phi_\mathrm{1PA}$ depends on the remaining contributions from the first-order GSF and the time-averaged components of the second-order GSF. The half-order correction $\Phi_\mathrm{res}$ arises due to the presence of self-forced $r\theta$-resonances experienced by EMRIs undergoing eccentric and inclined inspirals \cite{FlanHind12}. EMRI gravitational models must, therefore, include the $\Phi_\mathrm{0PA}$, $\Phi_\mathrm{res}$, and $\Phi_\mathrm{1PA}$ effects in order to maintain sub-radian phase accuracy and enable the full scientific potential of future mHz gravitational wave observatories.

Nonetheless purely adiabatic models---which only include $\Phi_\mathrm{0PA}$ in the gravitational wave phasing---may be suitable for detecting (but not characterizing) EMRI signals and are invaluable tools for developing data analysis pipelines for EMRI search and parametrization. They capture almost all of the phasing information and relativistic behavior of EMRI signals, making them powerful probes of astrophysical parameter space. The theoretical foundation and numerical calculation of adiabatic waveforms is also well understood, and has been performed for eccentric, precessing EMRIs \cite{HughETC21}.

@@

Therefore we introduce \texttt{bhpwave} [RTD link?] an open-source Python-based waveform generator that models the adiabatic dynamics and gravitational wave signals produced by a small body undergoing a quasi-circular\footnote{These inspirals are referred to as ``quasi-circular," because at any moment of time its motion is tangent to a circular geodesic as described in Sec.~\ref{sec:adiabatic}. This is a consequence of the fact that in the adiabatic limit, circular orbits remain circular, i.e., $e(t) = O(\epsilon)$ \cite{KennOri96, Kenn98}.} (non-eccentric) inspiral into a \emph{rotating} massive black hole. This code can model any binary with an initial orbital separation of $r_0 \leq 50 M$ and a massive black hole spin in the range $|a| \leq 0.995 M$. (See Sec.~\ref{sec:adiabatic} for exact definitions of $a$ and $r_0$.) Furthermore, the model supports any mass-ratio, though adiabatic waveform models are most relevant for $\epsilon \lesssim 10^{-4}$. By leveraging parallel computations across CPUs, \texttt{bhpwave} can evaluate years-long waveforms in milliseconds. Even on a standard laptop, waveform evaluations still complete within a few hundred milliseconds to a couple seconds.

@@

Additionally, \texttt{bhpwave} does not provide the first adiabatic calculation of quasi-circular inspirals. These systems have long been studied in the literature \cite{Detw78, KennOri96, FinnThor00, Hugh00b, GralHughWarb16}. However, as aforementioned, it is challenging to implement an adiabatic model that is efficient, reliable, and accessible. Even when neglecting eccentricity, the inclusion of massive black hole spin presents a number of challenges that are less pronounced for binaries with non-spinning bodies, such as the larger range of radial separations accessible to spinning binaries, the faster frequency evolution for more deeply bound orbits, and the higher mode content needed for modeling rapidly-rotating systems. By building upon the theoretical foundations described in the literature, our aim for \texttt{bhpwave} is to provide an efficient and accessible model that fills in this area of parameter space and provides an important stepping stone for developing more advanced models that incorporate all possible orbital effects.

@@

The mass $\mu$ follows a geodesic $z_p^\mu \doteq (t_p, r_p, \theta_p, \phi_p)$ that maintains a constant Boyer-Lindquist radius $r_p = r_0$ and is restricted to the equatorial plane $\theta_p = \pi/2$ (with respect to the angular momentum of the Kerr black hole). Due to the Killing symmetries of Kerr spacetime, this motion possesses three constants of motion: the orbital energy $u_t = - \mathcal{E}$, the $z$-component of the orbital angular momentum $u_\phi = \mathcal{L}_z$, and the Carter constant $\mathcal{Q} = Q_{\mu\nu} u^\mu u^\nu$ [citation], which are related to $a$ and $r_0$ by
\begin{subequations} \label{eqn:En}
\begin{align}
    \mathcal{E} &= \frac{1 - 2 v^2 \pm \hat{a} v^3}{\sqrt{1-3v^2\pm 2\hat{a}v^3}},
    \\
    \mathcal{L}_z &= \pm M  \frac{1 \mp 2 \hat{a} v^3 + \hat{a}^2 v^4}{v\sqrt{1-3v^2\pm 2\hat{a}v^3}},
    \\
    \mathcal{Q} &= 0,
\end{align}
\end{subequations}
where $\hat{a} \equiv a/M$, $v^2 = M/r_0$, and $+$ ($-$) refers to prograde (retrograde) orbits.

@@

The spin-weighted spheroidal harmonics can be conveniently represented as a rapidly-converging series of spin-weighted spherical harmonics $Y_{s\ell m}$ \cite{Hugh00b},
\begin{align}
    S_{sjm}(\theta, \gamma)e^{im\phi} = \sum_{\ell=\ell_\mathrm{min}}^\infty b_{sjm}^\ell(\gamma) Y_{s\ell m}(\theta,\phi),
\end{align}
where $\ell_\mathrm{min}=\mathrm{max}[|m|,|s|]$. This decomposition is particularly useful because it allows us to reproject $\psi_4$ onto an angular basis that is independent of frequency,
\begin{align} \label{eqn:psi4LModes}
    \psi_4 = \rho^{4} \sum_{\ell=2}^\infty \sum_{m=-\ell}^\ell X_{-2\ell m}(r) e^{-im\Omega_pt} Y_{-2\ell m}(\theta, \phi),
\end{align}
where
\begin{align} \label{eqn:XfromR}
    X_{-2\ell m}(r) \sum_{j=\ell_\mathrm{min}}^\infty b_{-2jm}^\ell(\gamma)R_{-2jm}(r).
\end{align}
Furthermore, the spin-weighted spherical harmonics form a complete and orthonormal set on basis functions of the unit sphere (for the same value of spin-weight),
\begin{align}
    \int Y_{s\ell m} \bar{Y}_{s\ell'm'} d\Omega = \delta_{l l'} \delta_{m m'}.
\end{align}

@@

For our point-particle source on a circular geodesic, the radial mode function $R_{-2jm}(r)$ have the asymptotic forms
\begin{subequations} \label{eqn:asympR}
\begin{align}
    R_{-2jm}(r\rightarrow r_+) &\simeq Z^\mathcal{H}_{-2jm} \Delta^{2} e^{-im k_p r_*},
    \\ 
    R_{-2jm}(r\rightarrow \infty) &\simeq Z^\mathcal{I}_{-2jm} r^{3} e^{+im\Omega_p r_*},
\end{align}
\end{subequations}
where $k_p = \Omega_p - \Omega_+$, $\Omega_+ = a/(2Mr_+)$, and the tortoise coordinate $r_*$ is given by the differential relation $dr_*/dr = (r^2+a^2)/\Delta$.
The amplitudes $Z^\mathcal{H/I}_{-2jm}$ are often referred to as \emph{Teukolsky amplitudes} and are constructed via the standard Green's function method, also known as the method of variation of parameters (see Sec.~III\,A in \cite{HughETC21} or \cite{DrasHugh06} for further details). From \eqref{eqn:XfromR}, we see that $X_{-2\ell m}$ then possesses the same asymptotic behavior as $R_{-2\ell m}$ in \eqref{eqn:asympR} but with modified amplitudes
\begin{align}
    Z^\mathrm{H/I}_{-2jm} \rightarrow X^\mathrm{H/I}_{-2\ell m} = \sum_{j=\ell_\mathrm{min}}^\infty b^\ell_{-2jm}(\gamma) Z^\mathrm{H/I}_{-2jm}.
\end{align}
As a final note, because $Z^\mathrm{H/I}_{-2jm}$ and  $X^\mathrm{H/I}_{-2\ell m}$ depend on the source motion, we can parametrize both amplitudes in terms of the orbital constants, e.g., $X^\mathcal{H/I}_{-2\ell m}= {X}^\mathcal{H/I}_{-2\ell m}(\Omega_p; a)$.

Upon obtaining $\psi_4$, we can then calculate the flux of energy that $\psi_4$ radiates away to infinity $\dot{E}^\mathcal{I}$ and the flux radiated down the black hole horizon $\dot{E}^\mathcal{H}$ \cite{TeukPres74}, 
\begin{subequations} \label{eqn:fluxes}
\begin{align}
    \dot{E}^\mathcal{I} &= \frac{1}{4\pi} \sum_{jm} \alpha_{jm}^\infty {|Z^\mathcal{I}_{-2jm}|^2},
    \\
    \dot{E}^\mathcal{H} &= \frac{1}{4\pi} \sum_{jm} \alpha_{jm}^\mathcal{H} {|Z^\mathcal{H}_{-2jm}|^2},
\end{align}
\end{subequations}
where 
\begin{align*}
    \alpha_{jm}^\mathcal{I} &= \frac{1}{m^2\Omega_p^2},
    \\
    \alpha_{jm}^\mathcal{H} &= \frac{256m^2 k_p\Omega_p(2Mr_+)^5(m^2k_p^2+4\epsilon^2)(m^2k_p^2+16\epsilon^2)}{|C_{2jm}|^2},
\end{align*}
$\epsilon = (r_+ - M)/(2Mr_+)$, and the Teukolsky-Starobinsky constant is given by
\begin{align} 
    |C_{2jm}|^2 &=\Lambda_{2j m }^2(\Lambda_{2j m }-2)^2
    \\ \notag
    & \quad + 8 a m^2 \Omega_p(1 - a \Omega_p)(\Lambda_{2j m }-2)(5\Lambda_{2j m }-4)
    \\ \notag
    & \quad \quad
    +48 (a m \Omega_p)^2[4(\Lambda_{2j m }-1)+3m(1- a \Omega_p)].
\end{align}
Note that the Chandrasekhar eigenvalue $\Lambda_{sjm} = \lambda_{sjm} + s(s+1)$ is invariant under the interchange $s\rightarrow -s$ \cite{Chan83}.
The angular momentum fluxes are then related to the energy fluxes by $\dot{L}_z^{\mathcal{I}/\mathcal{H}} = \Omega^{-1} \dot{E}^{\mathcal{I}/\mathcal{H}}$, leading to the total gravitational wave fluxes
\begin{align}
    \dot{E}^\mathrm{GW} &= \dot{E}^\mathcal{I} + \dot{E}^\mathcal{H},
    &
    \dot{L}_z^\mathrm{GW} &= \dot{L}_z^\mathcal{I} + \dot{L}_z^\mathcal{H}.
\end{align}

@@

Due to gravitational {radiation-reaction}, the small body does not remain on a circular geodesic. The binary \emph{radiates} gravitational waves and the small body \emph{reacts} to the radiative losses of energy and angular momentum by undergoing a quasi-circular inspiral into the rotating massive black hole. We can parametrize this motion in terms of the time-evolving orbital energy ${E}(t)$ and orbital phase $\Phi(t)$ of the inspiraling body, which at leading order is given by the equations of motion \cite{PounWard20,HughETC21},
\begin{align} \label{eqn:eom}
    \frac{d {E}}{dt} &= \epsilon \mathcal{F}_E + O(\epsilon^2),
    &
    \frac{d\Phi}{dt} &= \Omega + O(\epsilon).
\end{align}
Because $\dot{E} \sim \epsilon$, the orbital energy evolves gradually and the evolution can be understood in terms of the \emph{osculating geodesics} method \cite{GairETC11}. At any time $t_0$, the motion is approximately tangent to a geodesic with energy $E(t_0) \approx \mathcal{E}$ and frequency $\Omega(t_0) \approx \Omega_p$. The small body then evolves from geodesic to geodesic based on its gravitational wave emission until the body approaches the ISCO, at which point the approximation breaks down and we end the evolution.

In effect, at leading order we can express the orbital frequency $\Omega$ in terms of the orbital energy ${E}$ using Eqs.~\eqref{eqn:En} and \eqref{eqn:OmegaOfR}, but with $\mathcal{E}$ and $\Omega_p$ replaced by $E$ and $\Omega$, respectively. Furthermore, the forcing term $\mathcal{F}_E$ is constructed using flux-balance arguments \cite{Mino03, Galt82, QuinWald99}: for a point-particle on a circular geodesic the loss of orbital energy is balanced by the gravitational wave energy flux $\dot{E}^\mathrm{GW}$, leading to the relation $\epsilon \mathcal{F}_E = - \dot{E}^\mathrm{GW}$.

As seen from Eq.~\eqref{eqn:eom}, the time it takes the system to undergo this inspiral scales with the radiation reaction timescale $T_\mathrm{insp} \sim T_\mathrm{rr} = M \epsilon^{-1}$. Similarly, the total accumulated phase scales like $\Delta\Phi_\mathrm{insp} \sim \epsilon^{-1}$, thus giving the leading-order phase contribution to the gravitational wave signal, as described in Eq.~\eqref{eqn:twotimescale}.

@@

After determining the adiabatic inspiral of the smaller body, we generalize \eqref{eqn:psi4LModes}---our geodesic expression for $\psi_4$---by once again leveraging the fact that at any moment of time the motion is approximately tangent to a geodesic. Consequently, the field amplitudes are promoted from constants to quantities that slowly evolve with frequency and time $X^\mathcal{H/I}_{-2\ell m}(\Omega_p; a) \rightarrow X^\mathcal{H/I}_{-2\ell m}(\Omega(t); a)$, while the field's phase rapidly accumulates in proportion to the orbital phase $\Omega_p t \rightarrow \Phi(t)$. As a result, the adiabatic waveform $h = h_+ - i h_\times$ takes the form
\begin{align} \label{eqn:adiabaticWaveform}
    h(u,r,\theta,\phi) = \frac{\mu}{r}\sum_{\ell m} B_{\ell m}(u) Y_{-2\ell m}(\theta, \phi) e^{-im\Phi(u)},
\end{align}
where, assuming $r \gg M$, the waveform amplitudes are given by
\begin{align} \label{eqn:amplitude}
    B_{\ell m}(u) = -2\frac{X_{-2\ell m}^\mathcal{I}( \Omega(u);a)}{m^2\Omega^2(u)} = A_{\ell m} e^{i \psi_{\ell m}}.
\end{align}
For later convenience we introduce $A_{\ell m} = |B_{\ell m}|$, the magnitude of the waveform amplitudes, and $\psi_{\ell m}$, the phase of the complex amplitudes, both of which depend on $\Omega(u)$ and $a$. Furthermore, rather than using the conventions of \cite{KatzETC21,HughETC21}, we follow \cite{PounWard20} and parametrize the adiabatic waveform in terms of the outgoing time-coordinate $u=t-r_*$. As a result, if we hold the orbital constants and frequencies fixed, \eqref{eqn:adiabaticWaveform} reduces to a geodesic ``snapshot'' waveform obtained via \eqref{eqn:psi4ToH} and \eqref{eqn:psi4LModes}. In practice, when implementing \eqref{eqn:adiabaticWaveform} in \texttt{bhpwave}, we replace $u$ with Boyer-Lindquist time $t$ to match the FEW model (which is described by (10) in \cite{KatzETC21}). This is equivalent to parametrizing all of our waveforms with an initial time $t_0 = r_*$.

@@

The amplitude and phase decomposition of \eqref{eqn:adiabaticWaveform} makes it particularly straightforward to represent our waveforms in the frequency domain via the stationary phase approximation \cite{HughETC21},
\begin{align} \label{eqn:fourierH}
    \tilde{h}(f) &= \int_{-\infty}^\infty h(t) e^{2\pi i f t} dt,
    \\ \notag
    & \approx \frac{\mu}{r}\sum_{\ell m} \tilde{B}_{\ell m}(f) Y_{-2\ell m}(\theta, \phi) e^{i[2\pi f t_p(f)- m\Phi(t_p(f))]},
\end{align}
where
\begin{align} \label{eqn:fourierAmplitude}
    \tilde{B}_{\ell m}(f) \approx \sqrt{\frac{2\pi}{i m \dot{\Omega}[t_p(f)]}} {B}_{\ell m}(t_p(f)),
\end{align}
and $t_p(f)$ refers to the times at which the binary emits gravitational waves with frequency $f$. For each $(\ell, m)$-mode, time and frequency are approximately related by
\begin{align} \label{eqn:fourierPhase}
    2\pi f \approx m \dot{\Phi}(t) = m \Omega(t),
\end{align}
which we can invert to approximate $t_p(f)$ for individual harmonics. Both \eqref{eqn:fourierAmplitude} and \eqref{eqn:fourierPhase} neglect terms related to $\dot{\psi}_{\ell m}$ and $\ddot{\psi}_{\ell m}$, which introduces an $O(\epsilon)$ error to the phase and an $O(\epsilon^{1/2})$ error to the amplitude. (See Appendix \ref{app:fourierPhase} for further details.) Since the amplitudes scale as $\tilde{B}_{\ell m}(f) \sim 1/\sqrt{\epsilon}$, it is safe to neglect these terms for small mass-ratios.

@@

\subsection{Equations of motion and the numerical domain}
